Pushdown Control-Flow Analysis via Refunctionalization (Functional Pearl)

### 2018-03-14 paper.tex
code

\begin{lstlisting}
case class VS(vals: Set[Storable], time: Time, store: BStore)

type Ans = Set[VS]
type NCont = VS => Ans
type Cont = VS => (NCont => Ans)

def aval(e: Expr, env: Env, store: BStore, time: Time, cont: Cont, ncont: NCont): Ans = {
  val new_time = (e::time).take(k)
  e match {
    case Let(x, App(f, ae), e) =>
      val closures = aeval(f, env, store).toList.asInstanceOf[List[Clos]]

      def nd(closures: List[Clos]): Ans = {
        val Clos(Lam(v, body), c_env)::rest = closures
        val baddr = allocBind(v, new_time)
        val new_env = c_env + (v -> baddr)
        val new_store = store.update(baddr, aeval(ae, env, store))
        val new_cont = (vs: VS) => (r: NCont) => {
          val baddr = allocBind(x, vs.time)
          val new_env = env + (x -> baddr)
          val new_store = vs.store.update(baddr, vs.vals)
          aval(e, new_env, new_store, vs.time, cont, r)
        }
        val new_ncont = if (rest.isEmpty) {
          ncont
        } else (vs: VS) => {
          nd(rest) + vs
        }
        // new_time is determined by the lexical scope
        aval(body, new_env, new_store, new_time, new_cont, new_ncont)
      }

      nd(closures)
    case ae if isAtomic(ae) =>
      val ds = aeval(ae, env, store)
      cont(VS(ds, new_time, store))(ncont)
  }
}

def mtEnv = Map[String, BAddr]()
def mtStore = Store[BAddr, Storable](Map())
def analyze(e: Expr) = aval(e, env, store, List(), 
                            (vs: VS) => (r: NCont) => r(vs), 
                            (vs: VS) => Set(vs))

\end{lstlisting}

>>>>

\begin{lstlisting}
case class VS(vals: Set[Storable], time: Time, store: BStore)
type NCont = Set[VS] => Set[VS]
type Cont  = NCont => (Set[VS] => Set[VS])

def aval(e: Expr, env: Env, store: BStore, time: Time,
          cont: Cont, ncont: NCont): Set[VS] = {
  val new_time = (e::time).take(k)
  e match {
    case Let(x, App(f, ae), e) =>
      val closures = aeval(f, env, store).toList.asInstanceOf[List[Clos]]

      def new_ncont(ret_vss: Set[VS])(result: Set[VS]): Set[VS] = {
        val VS(vals, time, store) = ret_vss.head
        val baddr = allocBind(x, time)
        val new_env = env + (x -> baddr)
        val new_store = store.update(baddr, vals)
        aval(e, new_env, new_store, time, (r: NCont) => r, (vss1: Set[VS]) => {
          if (ret_vss.tail.isEmpty) cont(ncont)(result ++ vss1)
          else new_ncont(ret_vss.tail)(result ++ vss1)
        })
      }

      def nd(closures: List[Clos], vss_acc: Set[VS]): Set[VS] = {
        val Clos(Lam(v, body), c_env)::rest = closures
        val baddr = allocBind(v, new_time)
        val new_env = c_env + (v -> baddr)
        val new_store = store.update(baddr, aeval(ae, env, store))
        aval(body, new_env, new_store, new_time, (r: NCont) => r, (vss: Set[VS]) => {
          if (rest.isEmpty) new_ncont(vss_acc ++ vss)(Set())
          else nd(rest, vss_acc ++ vss)
        })
      }

      nd(closures, Set())

    case ae if isAtomic(ae) =>
      val ds = aeval(ae, env, store)
      cont(ncont)(Set(VS(ds, new_time, store)))
  }
}

def mtTime = List()
def mtEnv = Map[String, BAddr]()
def mtStore = Store[BAddr, Storable](Map())

def analyze(e: Expr) = aval(e, mtEnv, mtStore, mtTime, 
                            (r: NCont) => (vss: Set[VS]) =>  r(vss), 
                            (vss: Set[VS]) => vss)
\end{lstlisting}
